Homework

### 2016-07-02 Macro Impacts.tex
Trying this again
Displacements

0&=(\Sigma_xk_y-\Sigma_yk_x)^2\,.

@@

>>>>

0&=(\Sigma_{x}k_y-\Sigma_{y}k_x)^2\,.

@@

We now solve for $A_i$ in terms of $\Sigma_{i}$.
Now we take the curl of $A$ to find the shear mode displacement
U_x&=ky A_z-kz A_y\,,\\
&=\f{1}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}
Just cyclically permute the indices to obtain the expressions for $U_y$ and $U_z$.
